HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-03 paper/main.tex
abbreviating

To assess whether, HUME supports the reliable annotation of long sentences,
we binned the sentences according to length and measured Kappa on each of the
bins (\figref{fig:iaalength}).
%The Kappas for each bin is presented in 
%\figref{fig:iaalength}.
%Results show that there is
We see
no reduction of IAA with sentence
length, except perhaps in German. Also, from \tabref{tab:iaa} the overall IAA
is quite similar for all languages, showing good agreement (0.6--0.7).
However, there are differences observed when we break down by node type.
In particular, we see a contrast  between
Czech and Polish, where the IAA is higher for atomic than for structural units, and German and Romanian,
where the reverse is true. We also observe low IAA (around 0.3) in the cases of
German atomic units, and Polish and Czech structural units.

>>>>

To assess HUME reliability for long sentences,
we binned the sentences according to length and measured Kappa on each of the
bins (\figref{fig:iaalength}).
%The Kappas for each bin is presented in 
%\figref{fig:iaalength}.
%Results show that there is
We see
no reduction of IAA with sentence
length, except perhaps in German. Also, from \tabref{tab:iaa} the overall IAA
is quite similar for all languages, showing good agreement (0.6--0.7).
However, there are differences observed when we break down by node type.
In particular, we see a contrast  between
Czech and Polish, where the IAA is higher for atomic than for structural units, and German and Romanian,
where the reverse is true. We also observe low IAA (around 0.3) in the cases of
German atomic units, and Polish and Czech structural units.
